A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-20 fivebranes/index.tex

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \eeqn

  where . The BV pairing is given by

\end{prop}
\begin{proof}
Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.

@@

We
\end{proof}

>>>>

We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}. Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$. The situation is summarized in the diagram below.

@@

\surya{conditions for top left to be a vector bundle}

We claim that the splitting $\sigma$ induces a splitting $\mathring \sigma : h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}\to F_{\mathring M}$. \surya{is this obvious?} It is clear that $\mathring \sigma$ preserves lie brackets.

For brevity, let $F_{\mathring M/\R_{>0}\times Z} = F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}$ and $p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}$. Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{F_{\R_{>0}\times Z}}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{F_{\mathring M}}(\cL)\cong \cA^{\bu}_{F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{F_{{\mathring M/ \R_{>0}\times Z}}}\otimes \cL
\]

Accordingly, the differential splits

Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties. We may commute it past the tensor product above. Moreover, we may apply the functor term-wise. The result is that the pushforward is given by

In sum, we have proven the following:

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL))\right)
  \eeqn

  The BV pairing is given by
  \beqn
  \int_{}
  \eeqn

\end{prop}

### 2022-09-20 fivebranes/twisted.tex

There is also the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
Let $\theta_F$ be the bundle $T_M ^{\C} / F$ on $M$ and declare
$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
Then we obtain a resolution
\beqn
\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
\eeqn
The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.

>>>>

There is also the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
$\cA^k(\theta_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^k F^* \otimes \theta_F$.
Then we obtain a resolution
\beqn
\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
\eeqn
The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.
